---
title: "RCLIF_vitals"
output: html_document
date: "2023-07-03"
author: Kaveri Chhikara
---

```{r}
library(tidyverse)
library(bigreadr)
library(digest)
library(readxl)
library(arrow)
library(stringr)
```


```{r filepath}
vitals_flowsheet_path <- "/Users/kavenchhikara/Desktop/RCLIF/data/C19_FLOW_LDS_part1.txt"
vitals_flowsheet2_path <- "/Users/kavenchhikara/Desktop/RCLIF/data/C19_FLOW_LDS_part2.txt"
```

```{r load_vitals_in, eval=FALSE}
vitals_flowsheet  <- big_fread1(file = vitals_flowsheet_path, every_nlines=10000000)
vitals_flowsheet2 <- big_fread1(file = vitals_flowsheet2_path, every_nlines=10000000)
all_vitals <- rbind(vitals_flowsheet, vitals_flowsheet2)
rm(vitals_flowsheet)
rm(vitals_flowsheet2)
```


#### RCLIF scores
Obtaining relevant lab names from raw data 

Limited vocab-
GCS-eye, verbal, motor
RASS- Richmond Agitation-Sedation Scale. It is a tool used to assess a patient's level of sedation and agitation in critical care settings.,
CAM-ICU- Confusion Assessment Method for the Intensive Care Unit. It is a tool used to identify delirium in critically ill patients.
Braden- Braden Scale for Predicting Pressure Sore Risk. It is a tool used to assess a patient's risk of developing pressure ulcers (bedsores) based on various factors, including mobility, sensory perception, moisture, activity, nutrition, and friction/shear.

```{r}
score_names <- c("NUR RA GLASGOW ADULT SCORING",
                 "NUR RA GLASGOW ADULT BEST MOTOR RESPONSE",
                 "NUR RA GLASGOW ADULT EYE OPENING",
                 "NUR RA GLASGOW ADULT VERBAL RESPONSE")
```

```{r}
rclif_scores <- all_vitals %>% 
  filter(flo_meas_name %in% c(score_names)) %>%
  select(C19_PATIENT_ID, C19_HAR_ID, recorded_time, flo_meas_name, meas_value) %>%
  mutate(recorded_time = format(as.POSIXct(recorded_time, origin = "1970-01-01"),  "%Y-%m-%d %H:%M:%S")) %>% 
  rename(score_time = recorded_time,
         score_name = flo_meas_name,
         score_value = meas_value) %>% 
  arrange(C19_PATIENT_ID, score_time)
```

## write csv and parquet

```{r}
write.csv(rclif_scores, file="/Users/kavenchhikara/Desktop/RCLIF/output/RCLIF_scores.csv")
```

```{r}
write_parquet(rclif_scores,"/Users/kavenchhikara/Desktop/RCLIF/output/RCLIF_scores.parquet")
```



# Checks
```{r}
names(all_vitals)
```

```{r}
all_vitals %>% filter(str_detect(flo_meas_name, regex("RASS", ignore_case = TRUE))) %>% count(flo_meas_name)
```

## Calculate sofa neuro



```{r}
rclif_scores_sofa <- rclif_scores %>% 
  mutate(sofa_neuro = case_when(
           as.numeric(`NUR RA GLASGOW ADULT SCORING`) < 6 ~ 4,
           as.numeric(`NUR RA GLASGOW ADULT SCORING`) < 10 ~ 3,
           as.numeric(`NUR RA GLASGOW ADULT SCORING`) < 13 ~ 2,
           as.numeric(`NUR RA GLASGOW ADULT SCORING`) < 15 ~ 1,
           as.numeric(`NUR RA GLASGOW ADULT SCORING`) == 15 ~ 0
         )) 
```

