---
title: "RCLIF_disposition"
output: html_document
date: "2023-07-05"
author: Kaveri Chhikara
---

```{r}
library(tidyverse)
library(boxr)
library(survival)
library(bigreadr)
library(digest)
memory.limit(size = 30000)
```

# Pull Data from Box

These credentials come from a unique "interactive" box app that each user should create with their specific UCMC box login credentials, see [ vignette for how to use boxr](https://cran.r-project.org/web/packages/boxr/vignettes/boxr.html). These
specific ID and secret values have been loaded from a RData file that is not pushed
to GitHub.
```{r box_connection}
# load("hidden_codes.RData")
# boxr::box_fresh_auth()
box_auth(client_id = "8tiw6nuhzopcfgef9s9366lusndc0hf1", 
         client_secret = "WhxifwX8DVszZ8YNGufvMhKASeWxn3dg")
```

## Choose time period

```{r}
start_date <- "2022-01-01 00:00:00"
end_date <- "2022-02-01 00:00:00"
# admitted on or after Jan 1, 2022 and Before Feb 1, 2022
month <- "2022-01"
```

## Load data

```{r load_dispo_data, eval = FALSE}
dispo <- box_search("C19_ENC_XTRA_LDS.txt") %>% box_read()
```


Only include hospital billing observations and remove duplicates. 
```{r}
dispo_filtered <- dispo %>% 
  filter(record_type == "hb") %>% 
  select(C19_PATIENT_ID, C19_HAR_ID, discharge_dispo) %>% 
  arrange(C19_PATIENT_ID, C19_HAR_ID) %>% 
  subset(!duplicated(C19_PATIENT_ID, fromLast = TRUE))
```


```{r definitions}
#Definitions
home_categories <- c("Discharged/transferred to Home Under Care of Organized Home Health Service Org",
                     "Discharged to Home or Self Care (Routine Discharge)",
                     "Left Against Medical Advice or Discontinued Care",
                     "Left before treatment complete",
                     "Left without being seen")

death_categories <- c("Expired")

hospice_categories <- c("Hospice - Home",
             "Hospice - Medical Facility (Certified) Providing Hospice Level of Care")

admitted_categories <- c("Admitted as an Inpatient to this Hospital",
                         "Still Patient")
```

```{r}
dispo_filtered <- dispo_filtered %>% 
  mutate(disposition_name = case_when(
    discharge_dispo %in% death_categories ~ "Dead",
    discharge_dispo %in% hospice_categories ~ "Hospice",
    discharge_dispo %in% home_categories ~ "Home",
    grepl("^Discharged/transferred to", discharge_dispo) ~ "Discharged to another facility",
    discharge_dispo %in% "Disch/trans to Another Type of Health Care Inst not Defined Elsewhere in this List" ~ "Discharged to another facility",
    discharge_dispo %in% admitted_categories ~ "Admitted",
    TRUE ~ "Other"  # This will catch all other cases not matching the above conditions. This includes missing values, and Error on Registrations
  )) %>% 
  select(-c(discharge_dispo))
```

## Create new IDs
```{r}
dispo_clean <- dispo_filtered %>% 
  mutate(patient_ID = sapply(C19_PATIENT_ID , function(x) digest(x)),
         encounter_ID = sapply(C19_HAR_ID , function(x) digest(x))) %>% 
  select(patient_ID, encounter_ID, disposition_name)
```

## Write to CSV

```{r}
write.csv(dispo_clean, file="RCLIF_disposition.csv")
```

## Sanity checks

```{r}
#check number of duplicates
dispo_filtered %>%
  summarise(across(everything(), ~ sum(duplicated(.))))
```

