---
title: "RCLIF_dialysis"
author: "Rachel Baccile"
date: "2024-03-07"
output: html_document
---

```{r}
library(tidyverse)
library(boxr)
library(survival)
library(bigreadr)
library(digest)
memory.limit(size = 30000)
```

# Pull Data from Box

These credentials come from a unique "interactive" box app that each user should create with their specific UCMC box login credentials, see [ vignette for how to use boxr](https://cran.r-project.org/web/packages/boxr/vignettes/boxr.html). These
specific ID and secret values have been loaded from a RData file that is not pushed
to GitHub.
```{r box_connection}
# load("hidden_codes.RData")
# boxr::box_fresh_auth()
box_auth(client_id = "8tiw6nuhzopcfgef9s9366lusndc0hf1", 
         client_secret = "WhxifwX8DVszZ8YNGufvMhKASeWxn3dg")
```

## Load data

```{r load_flow_io_data, eval = FALSE}
flow_io <- box_search("C19_FLOW_IO_LDS.txt") %>% box_read()
```

## Filter to only dialysis related measurements
```{r filter_dialysis, eval = FALSE}

dialysis <- flow_io %>%
  filter(flo_meas_name %like% "DIALYSIS") %>%
  distinct()
rm(flow_io)
dialysis <- as.data.frame(dialysis)
```

# CRRT in RCLIF format
CRRT "Actual Fluid Removed (mL)" and "Fluid Delivered (L/Hr)" are documented every hour. CRRT starts 1 hour before "Actual Fluid Removed (mL)" and "Fluid Delivered (L/Hr)" are documented. CRRT ends at last "Actual Fluid Removed (mL)" and "Fluid Delivered (L/Hr)" documentation.
```{r crrt, eval = FALSE}

crrt_df <- dialysis %>% filter(flo_group_name=="Actual Fluid Removed (mL)" |
                                 flo_group_name=="Fluid Delivered (L/Hr)") %>%
                        select(C19_HAR_ID, flo_group_name, recorded_time, meas_value)


crrt_df_times <-  crrt_df %>%
                        select(C19_HAR_ID, recorded_time) %>%
                        distinct() %>%
                        group_by(C19_HAR_ID) %>%
                        arrange(C19_HAR_ID, recorded_time) %>%
                        mutate(start_time = recorded_time - hours(1)) %>%
                        distinct()
colnames(crrt_df_times) <- c("encounter_id", "stop_time", "start_time") 

removal_crrt <- crrt_df %>%
                    filter(flo_group_name=="Actual Fluid Removed (mL)")%>%
                    select(C19_HAR_ID, meas_value, recorded_time) %>% 
                    distinct()
colnames(removal_crrt) <- c("encounter_id", "ultrafiltration_amount", "stop_time") 

filtrate_crrt <- crrt_df %>%
                    filter(flo_group_name=="Fluid Delivered (L/Hr)")%>%
                    select(C19_HAR_ID, meas_value, recorded_time) %>% 
                    distinct()
colnames(filtrate_crrt) <- c("encounter_id", "dialysate_flow_amount", "stop_time") 


crrt_df_clif <- left_join(crrt_df_times, filtrate_crrt)
crrt_df_clif <- left_join(crrt_df_clif, removal_crrt)
crrt_df_clif$dialysis_type <- "crrt"

crrt_df_clif <- crrt_df_clif %>% select("encounter_id","dialysis_type", "start_time", "stop_time", "dialysate_flow_amount", "ultrafiltration_amount")
```

# Intermittent HD in CLIF format
Intermittent HD starts when "Machine Number" is documented. Intermittent HD ends at next documentation of "aUltra Filtration Net Loss".
```{r int, eval = FALSE}

int_df <- dialysis %>% filter(flo_group_name=="aUltra Filtration Net Loss" |
                                flo_group_name=="Machine Number") %>%
                      select(C19_HAR_ID, flo_group_name, recorded_time, meas_value)
int_df_times <-  int_df %>%
                      filter(flo_group_name=="aUltra Filtration Net Loss" |
                               flo_group_name=="Machine Number") %>%
                      select(C19_HAR_ID, flo_group_name, recorded_time) %>%
                      distinct() %>%
                      group_by(C19_HAR_ID) %>%
                      arrange(C19_HAR_ID, recorded_time) %>%
                      mutate(stop_time = lead(recorded_time)) %>%
                      filter(flo_group_name=="Machine Number") %>%
                      select(C19_HAR_ID, recorded_time, stop_time)
colnames(int_df_times) <- c("encounter_id", "start_time", "stop_time") 

removal_int <- int_df %>%
                filter(flo_group_name=="aUltra Filtration Net Loss")%>%
                select(C19_HAR_ID, meas_value, recorded_time) %>% 
                distinct()
colnames(removal_int) <- c("encounter_id", "ultrafiltration_amount", "stop_time") 


int_df_clif <- left_join(int_df_times, removal_int)
int_df_clif$dialysis_type <- "intermittent"

int_df_clif <- int_df_clif %>% select("encounter_id","dialysis_type", "start_time", "stop_time", "ultrafiltration_amount")
```



# Peritoneal Dialysis in CLIF format
Peritoneal Dialysis starts when "Initial Drain" or "Fill Volume" is documented. Peritoneal Dialysis ends at next documentation of "Total Ultrafiltration".

```{r peri, eval = FALSE}
peri_df_all <- dialysis %>% filter(flo_group_name=="Total Ultrafiltration"|
                                 flo_group_name=="Initial Drain" | flo_group_name=="Fill Volume") %>%
                        select(C19_HAR_ID, flo_group_name, recorded_time, meas_value) %>% 
                        distinct()
removal_peri <- peri_df_all %>%
                filter(flo_group_name=="Total Ultrafiltration"| flo_group_name=="Manual Exchange (Output)")%>%
                select(C19_HAR_ID, meas_value, recorded_time) %>% 
                filter(meas_value!=0) %>%
                distinct()

peri_df_start <-  peri_df_all %>%
                    filter(flo_group_name=="Initial Drain" | flo_group_name=="Fill Volume") %>%
                    select(C19_HAR_ID, flo_group_name, recorded_time) %>%
                    distinct() %>%
                    group_by(C19_HAR_ID) %>%
                    arrange(C19_HAR_ID, recorded_time) %>%
                    select(C19_HAR_ID, recorded_time) %>%
                    distinct()

peri_df_times <- bind_rows(peri_df_start, removal_peri)%>%
            arrange(C19_HAR_ID, recorded_time) %>%
            group_by(C19_HAR_ID) %>%
            mutate(stop_time = lead(recorded_time)) %>%
                    select(C19_HAR_ID, recorded_time, stop_time)
colnames(peri_df_times) <- c("encounter_id", "start_time", "stop_time") 
colnames(removal_peri) <- c("encounter_id", "ultrafiltration_amount", "stop_time") 


peri_df_clif <- left_join(peri_df_times, removal_peri) %>% filter(!is.na(stop_time))
peri_df_clif$dialysis_type <- "peritoneal"
```

# Merge all dialysis types for RCLIF_dialysis
```{r merge, eval = FALSE}

rclif_dialysis <- bind_rows(crrt_df_clif, int_df_clif)
rclif_dialysis <- bind_rows(rclif_dialysis, peri_df_clif)
```

# Sanity Checks

```{r check, eval = FALSE}
test <- rclif_dialysis %>% select(start_time, dialysis_type, encounter_id)
test$date <- as.Date(test$start_time)
test <- test %>% select(date, dialysis_type, encounter_id) %>% distinct()

test$year <- year(test$date)
test <- test %>% group_by(year, dialysis_type) %>% tally()
```

# Write data
```{r check, eval = FALSE}
write_parquet(rclif_dialysis, "RCLIF_dialysis.parquet")
write_csv(rclif_dialysis, "RCLIF_dialysis.csv")
```
